TODO: A Survey of StarCraft AI Techniques

### 2012-05-20 survey.tex
Changed "units control" to "unit control" in the figure and all over the paper (which is more correct in English)

\subsection{Units Control}
Units control, also called micro-management in RTS games, aims at maximizing the effectiveness of units, it starts with pathfinding and goes up to simultaneous control of units of different types in complex battles on heterogeneous terrain. The most common pathfinding algorithm is A*, but its big problem is CPU time and memory consumption, hard to satisfy in a complex, dynamic, real-time environment on multiple units. %To solve this the search space needs to be reduced as much as possible. 
A common technique consists in reducing the search into a navigation graph map. Among others, Triangulation Reduction A* computes polygonal triangulations on a grid-based map \cite{Demyen_2006}. One of the problems of A* related approaches in RTS games is that moving units block/get in the way of/ each others and the path has to be recomputed often. Craig Reynolds \cite{Reynolds_1999} introduced algorithmic steering behaviors, which simulate the aggregate motion of swarms. His model describes how a system of multiple agents, each steering according to simple local rules, can produce the collective movement found in flocks of birds. Danielsiek et al. \cite{Danielsiek_2008} studied intelligent squad movements to do tactical moves to flank the opponent in a RTS game this way. %An alternative to flocking is to use reciprocal velocity obstacles (RVO) \cite{Berg_2008}, since it is easier to control the behavior and they guarantee to prevent collisions. With this algorithm, we can move a large squad crossing another squad and avoid all possible collisions between units. {\color{blue}Do we put RVO? As I don't remember it being used in any game or game AI research.} (Santi: I agree, let's not mention it)
In recent commercial RTS games like Starcraft 2 or Supreme Commander 2, flocking-like behaviors are inspired of continuum crowds (``flow field'') \cite{Treuille2006}. A comprehensive review about (grid-based) pathfinding was recently done by Sturtevant \cite{sturtevant2012benchmarks}.

>>>>

\subsection{Unit Control}
Unit control, also called micro-management in RTS games, aims at maximizing the effectiveness of units, it starts with pathfinding and goes up to simultaneous control of units of different types in complex battles on heterogeneous terrain. The most common pathfinding algorithm is A*, but its big problem is CPU time and memory consumption, hard to satisfy in a complex, dynamic, real-time environment on multiple units. %To solve this the search space needs to be reduced as much as possible. 
A common technique consists in reducing the search into a navigation graph map. Among others, Triangulation Reduction A* computes polygonal triangulations on a grid-based map \cite{Demyen_2006}. One of the problems of A* related approaches in RTS games is that moving units block/get in the way of/ each others and the path has to be recomputed often. Craig Reynolds \cite{Reynolds_1999} introduced algorithmic steering behaviors, which simulate the aggregate motion of swarms. His model describes how a system of multiple agents, each steering according to simple local rules, can produce the collective movement found in flocks of birds. Danielsiek et al. \cite{Danielsiek_2008} studied intelligent squad movements to do tactical moves to flank the opponent in a RTS game this way. %An alternative to flocking is to use reciprocal velocity obstacles (RVO) \cite{Berg_2008}, since it is easier to control the behavior and they guarantee to prevent collisions. With this algorithm, we can move a large squad crossing another squad and avoid all possible collisions between units. {\color{blue}Do we put RVO? As I don't remember it being used in any game or game AI research.} (Santi: I agree, let's not mention it)
In recent commercial RTS games like Starcraft 2 or Supreme Commander 2, flocking-like behaviors are inspired of continuum crowds (``flow field'') \cite{Treuille2006}. A comprehensive review about (grid-based) pathfinding was recently done by Sturtevant \cite{sturtevant2012benchmarks}.
